The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-30 midterm/paper/main.tex
rename

\author{Hsieh Cheng-Han, Hsu Ting Hao, Sun Shih Yu}
\date{April 2023}
\maketitle

@@

  The result show that XXX is the most accurate on the prediction of diabetes.

@@

\section{Experiment result}
  This work compare the common classification algorithms, including KNN (with brute force, ANNOY-DFS, ANNOY-BFS), decision tree, 
  random forest, SVM (modified by GA), Neural Network, Naive Bayes classifier (modified by GA), PLA-pocket algorithm. 
  The programming language of KNN, decision tree, random forest and SVM-GA are C++20. And Neural Network, Naive Bayes classifier-GA 
  and PLA-pocket are using Python3 with pytorch and scikit-learn library. 
  Table \ref{table:overall} compares all datasets, which show that ...
  \begin{table*}[htb]
    %\normalsize
    %\centering
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques.}}
      \vspace{-\baselineskip}
    \begin{tabular}{@{}lccccccl@{}}\toprule
    Technique & Search (s) & testA & testA-normalized & testB & testB-normalized \\ \midrule
    KNN-Brute-Force  & $0.009$ & $76.6169 \pm \z{0}$                & $80.597 \pm 0$               & $78 \pm \z{0}$                 & $80 \pm \z{0}$\\
    KNN-ANNOY-DFS    & $0.003$ & $75.2438 \pm \z{1.8762}$           & $76.1294 \pm 2.0977$         & $74.9 \pm \z{2.5554}$          & $76.4 \pm \z{2.5377}$\\
    KNN-ANNOY-BFS    & $0.012$ & $76.6567 \pm \z{0.5340}$           & $80.597 \pm 0$               & $78.16 \pm \z{0.7310}$         & $80 \pm \z{0}$\\
    decision tree    & $0.009$ & $74.1294 \pm \z{0}$                & $74.1294 \pm 0$              & $76 \pm \z{0}$                 & $77 \pm \z{0}$\\
    random forest    & $0.004$ & $78.6965 \pm \z{1.751}$            & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
    SVM-GA           & $1.8462$ & $76.6616 \pm \z{4.0301}$          & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                  & $75 \pm \z{4}$\\
    Neural Network   & $3.2$   & $81.7910 \pm \z{2.0294}$           & $80.2985 \pm 1.4106$         & $78 \pm \z{1.6733}$            & $77.5 \pm \z{1.892}$\\
    Naive Bayes classifier-GA    & $X$ & $X \pm \z{X}$              & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\
    PLA-pocket       & $X$ & $X \pm \z{X}$                          & $X \pm X$                    & $X \pm \z{X}$                  & $X \pm \z{X}$\\ \midrule
    %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
    \end{tabular}
    \label{table:overall}
      \vspace{-\baselineskip}
  \end{table*}

\section{Conclusion}
  The experiment result shows that ...
\bibliographystyle{IEEEtran}
\bibliography{main}
\end{document}

>>>>

\author{Hsieh Cheng-Han, Hsu Ting-Hao, Sun Shih-Yu, Lu Che-Yuan, Huang Chia-Yen}
\date{April 2023}
\maketitle

@@

  The result show that KNN is the most accurate on the prediction of diabetes and balance the cost of time between accuracy, and since
  it is deterministic algorithm, it is very stable.

@@

\section{Experiment result}
  \begin{table*}[htb]
    %\normalsize
    %\centering
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques.}}
      \vspace{-\baselineskip}
    \begin{tabular}{@{}lccccccl@{}}\toprule
    Technique & Search (s)       & testA                              & testA-normalized             & testB                          & testB-normalized \\ \midrule
    KNN-Brute-Force  & $0.009$   & $76.6169 \pm \z{0}$                & $\bf{80.597 \pm 0}$          & $78 \pm \z{0}$                 & $\bf{80 \pm \z{0}}$\\
    KNN-ANNOY-DFS    & $0.003$   & $75.2438 \pm \z{1.8762}$           & $76.1294 \pm 2.0977$         & $74.9 \pm \z{2.5554}$          & $76.4 \pm \z{2.5377}$\\
    KNN-ANNOY-BFS    & $0.012$   & $76.6567 \pm \z{0.5340}$           & $\bf{80.597 \pm 0}$          & $\bf{78.16 \pm \z{0.7310}}$    & $\bf{80 \pm \z{0}}$\\
    decision tree    & $0.009$   & $74.1294 \pm \z{0}$                & $74.1294 \pm 0$              & $76 \pm \z{0}$                 & $77 \pm \z{0}$\\
    random forest    & $0.004$   & $78.6965 \pm \z{1.7510}$           & $78.5373 \pm 1.452$          & $77.98 \pm \z{2.083}$          & $77.5 \pm \z{2.516}$\\
    SVM-GA           & $1.846$   & $76.6616 \pm \z{4.0301}$           & $75.9219 \pm 2.736$          & $75 \pm \z{2}$                 & $75 \pm \z{4}$\\
    Neural Network   & $3.2$     & $\bf{81.7910 \pm \z{2.0294}}$      & $80.2985 \pm 1.4106$         & $78 \pm \z{1.6733}$            & $77.5 \pm \z{1.892}$\\
    Naive Bayes classifier-GA  & $14.29$ & $78.5353 \pm \z{0.0322}$   & $72.6866 \pm 0.0237$         & $77.4038 \pm \z{0.0626}$       & $71 \pm \z{0.0289}$\\
    PLA-pocket       & $0.00052$ & $63.682 \pm \z{0}$                 & $3.162 \pm 0$                & $63 \pm \z{0}$                 & $3.162 \pm \z{0}$\\ \midrule
    %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
    \end{tabular}
    \label{table:overall}
      \vspace{-\baselineskip}
  \end{table*}
  This work compare the common classification algorithms, including KNN (with brute force, ANNOY-DFS, ANNOY-BFS), decision tree, 
  random forest, SVM (modified by GA), Neural Network, Naive Bayes classifier (modified by GA), PLA-pocket algorithm. 
  The programming language of KNN, decision tree, random forest and SVM-GA are C++20. And Neural Network, Naive Bayes classifier-GA 
  and PLA-pocket are using Python3 with pytorch and scikit-learn library. 
  Table \ref{table:overall} compares all datasets, which show that KNN with brute force is the best method to predict 
  diabetes. And since it is deterministic algorithm, it is very stable. The only drawback is the time complexity is $O(n)$ where 
  $n$ is the number of the data points in dataset. But with ANNOY technique, the time complexity can be reduce to almost $O(\log n)$, 
  which solve the huge cost of brute force.

\section{Conclusion}
  Though PLA-pocket is the fastest method, the accuracy is not ideal. The neural network performs better, but it is not so stable. 
  While naive Bayes classifier modified by GA has surpurising good performance and stability, which can compete with random forests 
  in un-normalized dataset. The experiment result shows that KNN method fits best to early predict diabetes. 
  One thing to note that KNN performs better after normalized the dataset, while others perform the same or even worse, e.g. PLA-pocket. 
  The reason behind is normalization can make the data points scatter uniformly, which make KNN have better immunity to the wide gap 
  of data range.
\bibliographystyle{IEEEtran}
\bibliography{main}
\end{document}
